%-------------------------------------------------------------------------------
%   SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%   CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventryemp
    {Systems Engineer} % Job title
    {Client-FINRA} % Organization
    {Rockville, Maryland} % Location
    {May 2018 - Present} % Date(s)
    {Employer: Artech Information Systems(May 2018 - Present)}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Utilize specialized knowledge of Configuration Management tools like Puppet and Ansible, to identify and track individual configuration items, improve visibility and tracking across fleet of resources in AWS Cloud Infrastructure, hence enhancing system reliability.}
        \item {Write object oriented, time-space efficient and modularized Python code displaying strong experience and grasp of computer programming ethics by using well architected open source libraries and documenting code paradigms to automate infrastructure deployment, inject webhooks, auto-render manual code snippets, and enhance logging and monitoring.}
        \item {Lead architecting solution for managing several accounts in AWS(Amazon Web Services) cloud by ensuring real time compliance to Company’s policies, cost management via garbage collection of unused resources; Deploy resources in Cloud using CloudFormation scripts containing Dockerized Images and Containers in the form of Task and Service definitions, EC2(Elastic Compute Cloud) and IAM(Identity Access and Management) Credentials, Elastic Compute Clusters(ECS), Serverless Lambda and AWS CLI(Command Line) and API(Application Programming Interface) deployment.}
        \item {Design and develop automated solutions for distributed Linux/Unix server deployment and management by exploring and examining Artifact and Binary Repositories such as Artifactory, Nexus, performing load and performance testing using open source testing platform such as JMeter and in-house deployment tools, hence utilizing analyzed data to create effective and robust solutions.}
        \item {Streamline code and deployment pipeline by using Continuous Integration tools like Jenkins (JenkinsFile in Groovy/ MakeFile), integrated with JIRA agile development, accompanied with version control systems like BitBucket and documentation support on Confluence.}
        \item {Integrate ChatOps in the deployment and infrastructure pipeline using Slack customized notifications.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventryemp
    {Systems Engineer} % Job title
    {Client-CapitalOne} % Organization
    {McLean, Virginia} % Location
    {Oct. 2016 - April 2018} % Date(s)
    {Employers: Artech Information Systems(Oct 2017-April 2018), Core Software Technologies(April 2017-Oct 2017), Magnus Technology Solutions(Oct 2016-March 2017)}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Centralized Cloud Custodian policy development at the Enterprise level to achieve consistency, security and cost-effectiveness in AWS Cloud Infrastructure.}
        \item {Develop, test and maintain functionalities in Cloud Custodian to support encryption, tagging, backups, off-hours, network security for all services in AWS Cloud.}
        \item {Develop backend for Cloud Custodian Dashboard consuming data from SQS and indexing in Elasticsearch using Python ElasticSearch API.}
        \item {Maintain clear and up-to-date documentation for Internal Cloud Custodian policies using GitHub Pages.}
        \item {Design effective Jinja2 templates to notify and educate end users to safely use AWS Infrastructure.}
        \item {Deploy Jenkins jobs to enable push button deployment of Docker Images to keep infrastructure synced with new updates.}
        \item {Deploy new Services like Sentry Error Traking in AWS Elastic Container Services using CloudFormation Task and Service Definitions, ECS Clusters and Custom Docker images.}
        \item {Fix bugs reported by contributors on the Public Github Repository, communicate on the Issues on Public Github, peer review Code in the Pull Requests on Public and Private Repositories, actively partipate on Project's Gitter conversations}
        %\item {Write Python scripts to automate weekly and monthly reports.}
        \item {Monitor status of application by following on-call rotations using PagerDuty, involve Technical Operations to work with other teams during rotations.}
        \item {Train and Develop new associates on using CapitalOne open source projects, underlying infrastructure and team culture.}
        \item {Actively participate in Agile meetings like PI Planning, Retrospective, Daily standups and Deep Dive sessions, to effictively work with the team and complete assigned tasks.}
        \item {Provide email and phone support to other Software Engineers about securely and efficiently using AWS Infrastructure.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Network Engineer Intern} % Job title
    {Kamla Hotels} % Organization
    {Downey, California} % Location
    {May 2015 - Aug. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Analyzed and fixed complex software and hardware matters of significance pertaining to networking connectivity issues.}
        \item {Checked with user guides, technical manuals to find solutions and develop skills in testing network topologies.}
        \item {Installed and repaired routers and switches by referring to Manufacturer's handbook, install softwares onto new PCs, Laptops or Phones to help onboard new employees.}
        \item {Optimized search results for Company's chain of Hotels by using Search Engine Optimization, implemented by posting articles and blogs containing specific keywords.}
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {Student Desktop Support} % Job title
    {California State University, Long Beach} % Organization
    {Long Beach, California} % Location
    {Feb 2015 – May 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Installed, repaired, replaced and upgraded IT equipment including PCs, Laptops and Printers.}
        \item {Held sessions on MS Office, Windows tutorials and University's custom tools and databases for end users in multiple departments.}
        \item {Collected, systemized and recorded problem and solution logs.}
        \item {Provided ongoing support to users regarding systems and networks.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
